R for Clinical Study Reports and Submission

### 2021-11-01 submission-package.Rmd
correct adrg full name

In this chapter, we will first give a high-level overview of what
assets in the eCTD submission package we should focus on when
submitting R code.
Secondly, we will discuss how to prepare the proprietary R packages
(if any), and make them part of the submission package.
Lastly, we will provide reusable templates for updating
ADaM Reviewer's Guide (ADRG) and Analysis Results Metadata (ARM)
so that the reviewers receive proper instructions to reproduce the
analysis results.

@@

- ADaM data in `.xpt` format: created by SAS or R.
- `define.xml`: created by Pinnacle 21.
- ADRG (ADaM Reviewer's Guide)
  - "Macro Programs" section: provide R and R package versions with a snapshot date.
  - Appendix: provide step-by-step instructions for reviewers to
    reproduce the running environment and rerun analyses.
- ARM (Analysis Results Metadata): provide the links between TLFs and
  analysis programs in tables.

>>>>

In this chapter, we will first give a high-level overview of what
assets in the eCTD submission package we should focus on when
submitting R code.
Secondly, we will discuss how to prepare the proprietary R packages
(if any), and make them part of the submission package.
Lastly, we will provide reusable templates for updating
Analysis Data Reviewer's Guide (ADRG) and Analysis Results Metadata (ARM)
so that the reviewers receive proper instructions to reproduce the
analysis results.

@@

- ADaM data in `.xpt` format: created by SAS or R.
- `define.xml`: created by Pinnacle 21.
- ADRG (Analysis Data Reviewer's Guide)
  - "Macro Programs" section: provide R and R package versions with a snapshot date.
  - Appendix: provide step-by-step instructions for reviewers to
    reproduce the running environment and rerun analyses.
- ARM (Analysis Results Metadata): provide the links between TLFs and
  analysis programs in tables.
